### 2019-08-06 reports/thesis/chapters/3_compoundPoisson.tex
Added method of moments

The method of moments is a simpler method to estimate the parameters of a compound Poisson-gamma random variable. Suppose $\widehat{\mu}_1$ is an estimator of $\expectation[X]$ and $\widehat{\mu}_j$ is an estimator of $\expectation\left[\left(X-\expectation[X]\right)^j\right]$ for $j=2,3$. Then the estimators
\begin{equation}
  \widehat{\lambda}=\frac{\widehat{\mu}_1^2\widehat{\mu}_2}{2\widehat{\mu}_2^2-\widehat{\mu}_1\widehat{\mu}_3}
\end{equation}
\begin{equation}
  \widehat{\alpha}=\frac{2\widehat{\mu}_2^2-\widehat{\mu}_1\widehat{\mu}_3}{\widehat{\mu}_1\widehat{\mu}_3-\widehat{\mu}_2^2}
\end{equation}
\begin{equation}
  \widehat{\beta}=\frac{\widehat{\mu}_1\widehat{\mu}_2}{\widehat{\mu}_1\widehat{\mu}_3-\widehat{\mu}_2^2}
\end{equation}
are method of moments estimators of $\lambda$, $\alpha$ and $\beta$ respectively \citep{withers2011compound}. These estimators suffer because estimation is not done through the sufficient statistics and can be negative, this is a problem because the parameters do not take non-positive values.

>>>>

The method of moments is a simpler method to estimate the parameters of a compound Poisson-gamma random variable. Suppose $\widehat{\mu}_1$ is an estimator of $\expectation[X]$ and $\widehat{\mu}_j$ is an estimator of $\expectation\left[\left(X-\expectation[X]\right)^j\right]$ for $j=2,3$. Then the estimators
\begin{equation}
  \widehat{\lambda}=\frac{\widehat{\mu}_1^2\widehat{\mu}_2}{2\widehat{\mu}_2^2-\widehat{\mu}_1\widehat{\mu}_3}
\end{equation}
\begin{equation}
  \widehat{\alpha}=\frac{2\widehat{\mu}_2^2-\widehat{\mu}_1\widehat{\mu}_3}{\widehat{\mu}_1\widehat{\mu}_3-\widehat{\mu}_2^2}
\end{equation}
\begin{equation}
  \widehat{\beta}=\frac{\widehat{\mu}_1\widehat{\mu}_2}{\widehat{\mu}_1\widehat{\mu}_3-\widehat{\mu}_2^2}
\end{equation}
are method of moments estimators of $\lambda$, $\alpha$ and $\beta$ respectively \citep{withers2011compound}, this is shown in Appendix \ref{chapter:appendix_methodofmoments} These estimators suffer because estimation is not done through the sufficient statistics and can be negative, this is a problem because the parameters do not take non-positive values.
